State-space PTA

### 2023-04-20 docs/manuscript/paper.tex
assorted clean up

\noindent Interpreting the likelihood ratio $\Lambda$ also needs some consideration, since we have to account for the increased model complexity of $M_1$. Bayes factors penalise complexity by construction since one must integrate over a larger parameter space. There are many different ways to do this, AIC, BIC, Wilks Theorem... \newline

@@

\begin{figure*}
	\includegraphics[width=0.8\textwidth]{images/snr_mollewide}
	\caption{stuff}
	\label{fig:mollewide}
\end{figure*}

>>>>

\noindent Interpreting the likelihood ratio $\Lambda$ also needs some consideration, since we have to account for the increased model complexity of $M_1$. Bayes factors penalise complexity by construction since one must integrate over a larger parameter space. There are many different ways to do this - fot now we will consider two: Akaike information criterion (AIC) and Wilks Theorem. For the latter, Wilks' Theorem which states that for a large number of samples \footnote{What counts as large? See \url{https://www.osti.gov/servlets/purl/1529145}} the distribution of the test statistic approaches the chi-squared distribution under the null hypothesis i.e. 
\begin{equation}
	2 \log \Lambda \rightarrow \chi^2
\end{equation}
One can then compute $p$-values where the number of degrees of freedom is equal to the difference in the number of parameters of the two models; $M_1$ has 7 extra parameters over $M_0$ corresponding to the 7 parameters of $\bar{\theta}_{\rm GW}$. With 7 degrees of freedom and a target tolerance of 5(1) \% the test statistic is $\sim 14 (18.5)$. \newline

An alternative approach is to use the AIC which is given by,
\begin{equation}
	\text{AIC} = 2k - 2\log\ \mathcal{L} 
\end{equation}
where $k$ is the number of degrees of freedom. The AIC can be computed for each model and the model with the minimum AIC is preferred. This can be straightforwardly mapped into a relative condition
\begin{equation}
	\log \mathcal{L}_1 - 	\log \mathcal{L}_0 > 7 
\end{equation}
Note this is the same as the Wilks case!

@@

\begin{figure*}
	\includegraphics[width=0.8\textwidth]{images/snr_mollewide}
	\caption{\textcolor{red}{TK: Just a placeholder. Likelihood ratio for a given $h$. Maybe more interesting, but more expensive, to get minimum detectable h?}}
	\label{fig:mollewide}
\end{figure*}
